\subsection{Android User}
    Individual Module Testing will be left to the coder, and tests should be written before the coding is done.

    \begin{landscape}
        \begin{longtable}{|r|l|p{4cm}|p{4cm}|p{4cm}|p{4cm}|}
        \hline
        Test Ref & Req & Test Content & Input & Output & Pass \\ \hline
        SE-F-001 & FR1 & Startup of Software & Touch App logo & Botany App should open & Android app opens to the users activity. \\ \hline
        SE-F-002 & FR2 & Valid username allows user to login & Enter valid username of size 3\textless Username\textless 10 e.g Alexander & No error message appears & App proceeds to specimen activity. \\ \hline
        SE-F-003 & FR2 & Invalid username does not allow user to login & Enter username that is outside of the required length eg ``ab'' or ``asdfghjklqw'' 10 & App should display an error indicating correct lenghts & An error message in a box should pop up saying that the username has to be between 3 and 10 characters long.  \\ \hline
        SE-F-004 & FR2 & Empty Username is not accepted & Have the username empty & An error message shows next to the input & User is told of the error and the app does not proceed \\ \hline
        SE-F-005 & FR2 & Valid phone number is accepted & Enter a valid phone number e.g. 07808369246 & Along with a valid email and username the user can go to the next part of the app & An error message does not show next to the input and the user moves on \\ \hline 
        SE-F-006 & FR2 & Empty phone number is not accepted & Have the phone number empty & An error message shows next to the input & User is informed of the error and the app does not proceed \\ \hline
        SE-F-007 & FR2 & Invalid phone number is not accepted & Enter an invalid phone number e.g ``a'' & An error message shows next to the input & User is informed of the error and the app does not proceed \\ \hline
        SE-F-008 & FR2 & Valid email is accepted & Enter a valid email address e.g. this@that.com & Along with a valid phone number and username the user can go to the next part of the app & The app proceeds to the specimen adder activity \\ \hline
        SE-F-009 & FR2 & Empty Email is not accepted & Have the email address empty & An error message shows next to the input & User is informed of the error and the app does not proceed \\ \hline
        SE-F-010 & FR2 & Invalid email is not accepted & Enter an invalid email address e.g. this@that & An error message shows next to the input & User is informed of the error and the app does not proceed \\ \hline 
        SE-F-011 & FR2 & App gets the GPS information from the phone & User waits for valid GPS signal & Message is shown to say that a valid GPS signal has been found & User is allowed to move on without entering a site name \\ \hline
        SE-F-012 & FR2 & Site name is accepted & User enters the name of the site e.g Aberystwyth & No error is displayed, the app moves to the speicmen adder & User is allowed to move on \\ \hline
        SE-F-013 & FR3 & Latin name auto-completes & User enter the first four letters of a latin name e.g. gara & A list of all the Latin names with the input appears & All the Latin names that appear all have the input in them \\ \hline
        SE-F-014 & FR4 & Plant photo button works & User touches the plant photo button & User's phone goes to the inbuilt camera & User able to take picture with inbuilt camera \\ \hline 
        SE-F-015 & FR4 & Site photo button works & User touches the site photo button & User's phone goes to the inbuilt camera & User able to take picture with inbuilt camera \\ \hline
        SE-F-016 & FR4 & Plant photo is saved & User takes a plant photo & Picture is taken and takes the place of the plant photo button & The photo is saved, and ready to be submitted \\ \hline
        SE-F-017 & FR4 & Site photo is saved & User take site photo & Picture is taken and takes the place of the  site photo button & The photo is saved ready to be submitted \\ \hline
        SE-F-018 & FR4 & User not allowed to add a non-image file when prompted for a picture of a plant. & Attempt to enter a non-image file to the database. & Message states that the file is not an image file. & Does not enter to database. Returns to input page. \\ \hline
        SE-F-019 & FR4 & User not allowed to add a picture of a plant to the database if over 10MB &  Attempt to enter an absurdly large image file to the database (e.g 20MB). & States that the file exceeds filesize limits. & Does not enter to database. Returns to input page. \\ \hline
        SE-F-020 & FR4 & User allowed to edit abundance & User slides the abundance slider & The abundance slider moves & The abundance is changed and recorded \\ \hline
        SE-F-021 & FR3 & User allowed to add a plant name to the database. & Enter plant name to the database via android app. & States that plant details are successfully added to the database. & Plant details successfully added to the database. \\ \hline
        SE-F-022 & FR4 & User allowed to add Species Details. & Enter Species Details to the database via android app. & States that plant details are successfully added to the database. & Plant details successfully added to the database. \\ \hline
        SE-F-023 & FR4 & User not allowed to enter invalid Species Details to the database. & Enter invalid Species Details to the database via android app. & App states that the details entered are invalid. & Does not enter to database. Returns to input page. \\ \hline
        SE-F-024 & FR4 & User allowed to add a picture of a plant to the database. & Enter a plant picture to the database via android app. & States that plant picture is successfully added to the database. & Plant picture successfully added to the database. \\ \hline
        SE-F-025 & FR6 & Application should know whether it is connected to the internet, and that it is able to send records to the database. If not, the data is stored in local storage. & Attempt to do SE-F-004/5/7/10 whilst connected to the internet. & Pop-up states that records successfully sent to the database. & Successfully sends records to the database. \\ \hline
        SE-F-026 & FR6 & Application should know whether it is connected to the internet, and that it is able to send records to the database. If not, the data is stored in local storage. & Attempt to SE-F-004/5/7/10 whilst not connected to the internet. &  Pop-up states that the app is not connected to the internet and that the records were stored in local storage. & Stores the records on local storage. \\ \hline
        \end{longtable} 
    \end{landscape}

\subsection{Website User}
    Individual Module Testing will be left to the coder, and tests should be written before the coding is done.

    \begin{landscape}
        \begin{longtable}{|r|l|p{4cm}|p{4cm}|p{4cm}|p{4cm}|}
        \hline
        Test Ref & Req & Test Content & Input & Output & Pass Criteria \\ \hline
        SE-F-030 & FR8 & Editing reserve with one value changed & Grid reference change. & Reserve grid reference updated & Reserve data is able to be edited providing valid data. \\ \hline           
        SE-F-031 & FR8 & Edit all of the values of a reserve & All data changed to new valid data. & Reserve data updated & Reserve data is able to be editted providing valid data. \\ \hline          
        SE-F-032 & FR8 & Edit reserve with blank field & Remove data for one field and submit. & Reserve was not updated & Reserve data is able to be editted providing valid data and all fields filled. \\ \hline         
        SE-F-033 & FR8 & Add reserve name & Input reserve name for field. & Reserve name added & Reserve data is able to be added providing valid data and all fields filled.\\ \hline  
        SE-F-034 & FR8 & Add OS grid reference  & Input 8 digit OS grid reference. & Grid reference was added & Reserve data is able to be added providing valid data and all fields filled. \\ \hline  
        SE-F-035 & FR8 & Add reserve description  & Input reserve description. & Description was added & Reserve data is able to be added providing valid data and all fields filled. \\ \hline 
        SE-F-036 & FR9 & View reserve specimens & Click on view reserve button. & User is taken to the plant specimens page where only the reserve specimens contained within the reserve are displayed & Specimens that are contained within reserve are displayed.\\ \hline   
        SE-F-037 & EF1 & Authentication & Log in using correct password. & Authentication session is created giving user administrative privileges. A message displays valid password. & Password session is created and a successful login message is displayed.\\ \hline  
        SE-F-038 & EF1 & Authentication  Error & Log in using incorrect password. & A message displays incorrect password. & Password session is not created, and incorrect login message is displayed.\\ \hline    
        SE-F-039 & EF1 & Authentication logout& Logout link is clicked. & Session is destroyed and login message is displayed. & Session is destroyed and login message is displayed.\\ \hline  
        SE-F-040 & EF1 & Authentication granted privileges & User has successfully logged on & User is given access to delete remove and add specimens and reserves. & Session is destroyed and login message is displayed. \\ \hline
        SE-F-041 & EF2 & Add species name & Input species name & Species name is added to the record & Species name is added to the species record.\\ \hline
        SE-F-042 & EF2 & Add species location & User selects a reserve location & Reserve is identified with the species  & Once reserve is selected, the specimen is identified with the reserve .\\ \hline
        SE-F-043 & EF3 & Add specimen abundance & User selects a abundance according to the DAFOR scale & Abundance is recorded to the specimen & Abundance from the DAFOR scale is recorded to the specimen .\\ \hline
        SE-F-044 & EF3 & Add comment & User inputs comment & The comment is recorded & Comment is recorded to the specimen .\\ \hline
        SE-F-045 & EF3 & No comment & No input & Comment is left as NULL & Specimen comment is left null .\\ \hline
        SE-F-046 & EF3 & No image & No images are inputted & Image is not uploaded for the specimen & Specimen is recorded without an image .\\ \hline
        SE-F-047 & EF3 & PNG image & PNG image is uploaded & PNG image is uploaded & PNG image is recorded to the specimen .\\ \hline
        SE-F-048 & EF3 & GIF image & GIF image is uploaded & GIF image is uploaded & PNG image is recorded to the specimen .\\ \hline
        SE-F-049 & EF3 & JPEG image & JPEG image is uploaded & JPEG image is uploaded & JPEG image is recorded to the specimen .\\ \hline
        SE-F-050 & EF3 & Non-image type & txt file is uploaded & file is not uploaded & File is not uploaded . \\ \hline
        SE-F-051 & EF4 & Delete specimen & Delete specimen button is clicked & Specimen is deleted & Once clicked, the specimen is deleted. \\ \hline
        SE-F-052 & EF4 & Edit specimen & Specimen field is edited & Specimen field in question is edited & Specimen field is edited and is recorded to the specimen ID  . \\ \hline
        SE-F-053 & Features & Simple search bar & Inputted species name & User is taken to the specimen page with results displayed & Once submitted, user is shown specimens that match the search criteria  . \\ \hline
        SE-F-054 & Features & Advanced search bar with species name option selected& Species name with species selected & Results with specimen name displayed & Search results with matching criteria displayed only. \\ \hline
        SE-F-055 & Features & Advanced search bar with location option selected & The location input with location option selected & Results with inputted location displayed & Search results with matching criteria displayed only.\\ \hline
        SE-F-056 & Features & Advanced search bar with date option selected & Recording date input with date option selected & Results matching input and option displayed & Search results with matching criteria displayed only. \\ \hline
        SE-F-57 & Species sorting & Each sorting option selected & Sorting option is selected with sorting criteria & Table results are displayed and sorted to the matching criteria & Once the sorting method is chosen, the results are sorted. \\ \hline
        SE-F-058 & Features & Google Map & Correct latitude and  longitude & Map displays location on a Google maps & Google map should show the location of the specimen.\\ \hline
        SE-F-059 & Features & Google Map & Incorrect latitude and  longitude & Map displays nothing & Google map should show the location of the specimen. \\ \hline
        \end{longtable}

        \begin{longtable}{|r|l|p{4cm}|p{4cm}|p{4cm}|p{4cm}|}
            \hline
            Test Ref & Browser & Results\\ \hline
            SE-F-060 & Chrome & Displays the website perfectly and all functionality works on it.\\ \hline
            SE-F-061 & Firefox & Displays as it should mostly, apart from the about page due to an incompatibility with columns. Functions as it is supposed to. \\ \hline
            SE-F-062 & IE  & Displays correctly, apart from that the default images are not displayed. Functionality still correct. \\ \hline
            
        \end{longtable}
    \end{landscape}

\subsection{Server}
    Individual Module Testing will be left to the coder, and tests should be written before the coding is done.

    \begin{landscape}
        \begin{longtable}{|r|l|p{4cm}|p{4cm}|p{4cm}|p{4cm}|}
        \hline
        Test Ref & Req & Test Content & Input & Output & Pass Criteria \\ \hline
        SE-F-070 & FR7 & Server allows an addition of a valid record via a POST request) & Valid JSON-formatted record via POST & Returns status code 200 OK and ID of the record & Status code 200 OK and record present in the database \\ \hline
        SE-F-071 & FR7 & Server does not allow an addition of an invalid record via a POST request) & Invalid JSON-formatted record via POST & Returns status code 400 & Status code 400 and record not present in the database \\ \hline
        SE-F-072 & FR7 & Server allows an addition of a file resource via a POST request & A binary file via POST & Returns status code 200 OK and ID of the resource & Status code 200 OK and file present on server \\ \hline
        SE-F-073 & FR7 & Server allows client to get a specimen with a specified specimen ID that does exist& A POST request with the desired ID specified & Returns status code 200 OK and a JSON-formatted specimen & Status code 200 OK and a valid JSON-formatted specimen \\ \hline
        SE-F-074 & FR7 & Server does not allow the client to get a specimen with a specified specimen ID that does not exist & A POST request with the desired ID specified & Returns status code 400 & Status code 400, nothing returned  \\ \hline
        SE-F-075 & FR7 & Server allows client to get a file resource with a specified resource ID that exists & A POST request with the desired ID specified & Returns status code 200 OK and a file & Status code 200 OK and the desired file \\ \hline
        SE-F-076 & FR7 & Server does not allow the client to get a file resource with a specified resource ID that does not exist & A POST request with the desired ID specified & Returns status code 400 & Status code 400 no file returned \\ \hline
        SE-F-077 & FR7 & Server allows client to get a number of specimens based on a specified offset and range & A POST request with desired offset and range & Returns status code 200 OK, desired number of specimens starting from desired offset are returned as a valid JSON-formatted specimen & Status code 200 OK and an array of valid specimens, limited by desired range and offset \\ \hline
        SE-F-078 & FR7 & Server allows client to get a number of specimens based on a specified search value by name, user, location, reserveID & A POST request with desired search value and search type & Returns status code 200 OK, only desired specimens based on search value and search type are returned as a valid JSON-formatted specimen array & Status code 200 OK and an array of valid specimens, limited by search value and search type \\ \hline
        SE-F-079 & FR7 & Server allows client to get a number of specimens based on a specified search value by name, user, location and searched by reserveID & A POST request with desired search value and search type and specified reserveID & Returns status code 200 OK, only desired specimens based on search value, search type and reserveID are returned as a valid JSON-formatted specimen array & Status code 200 OK and an array of valid specimens, limited by search value, search type and reserveID \\ \hline
        SE-F-080 & FR7 & Server allows client to get a number of specimens ordered by ascending or descending and values name, user, abundance, location & A POST request with desired order method and order type & Returns status code 200 OK, all specimens ordered by desired order method and order type are returned as a valid JSON-formatted specimen array & Status code 200 OK and an array of valid specimens, ordered by desired order type and order value \\ \hline
        SE-F-081 & FR7 & Server allows client to get a number of specimens based on a specified search value by name, user, location, reserveID and ordered by ascending or descending and values name, user, abundance, location & A POST request with desired search value, search type, order method and order value & Returns status code 200 OK, only desired specimens based on search value and search type are returned as a valid JSON-formatted specimen array ordered by desired order type and order value & Status code 200 OK and an array of valid specimens, limited by search value and search type, ordered by order method and order type \\ \hline
        SE-F-082 & FR7 & Server allows client to get a number of specimens based on a specified search value by name, user, location and searched by reserveID and ordered by ascending or descending and values name, user, abundance, location & A POST request with desired search value, search type, reserveID, order method and order value & Returns status code 200 OK, only desired specimens based on search value, search type and reserveID are returned as a valid JSON-formatted specimen array ordered by desired order type and order value & Status code 200 OK and an array of valid specimens, limited by search value and search type, ordered by order method and order type \\ \hline
        SE-F-083 & FR7 & Server allows client to get a number of specimens, filtered by record location name & A POST request with the desired location name specified & Returns status code 200 OK and a JSON-formatted array of relevant records found & Status code 200 OK and an array of valid relevant records with same or similar location name \\ \hline
        SE-F-084 & FR7 & Server allows client to remove a specified specimen with a specified valid specimen ID &  A POST request with the desired specimen ID to be deleted &  Returns status code 200 OK &  Status code 200 OK and the specimen is removed from the database \\ \hline
        SE-F-085 & FR7 & Server does not allow client to remove a specified specimen with a specified specimen ID that is invalid&  A POST request with the desired specimen ID to be deleted &  Returns status code 400 &  Status code 400 and the specimen is not removed from the database \\ \hline
        SE-F-086 & FR7 & Server allows client to edit a specified specimen with a specified valid ID & A POST request with the desired ID and a JSON-formatted specimen & Returns status code 200 OK  & Status code 200 OK and specimen is changed in the database \\ \hline
        SE-F-087 & FR7 & Server does not allow client to edit a specified specimen with a specified invalid ID & A POST request with the desired ID and a JSON-formatted specimen & Returns status code 400  & Status code 400 and specimen is not changed in the database \\ \hline
        SE-F-088 & FR7 & Server does not allow client to enter any malicious data into the database & A POST request with malicious data & Returns status code 500 & Status code 500 and no data is affected in the database \\ \hline
        \end{longtable}
    \end{landscape}
