\subsubsection{Week One}
	This was the first time the group had met. Everyone introduced themselves and what degree they were taken, where we got a taste of what strengths each of us have and also each of or weaknesses in relation to the project. GitHub accounts need to be created as well as a new repo to be made. We spoke about the different roles and the work that needed to be done by the next week was what roles each individual wanted to do and to read the project requirements and QA documents.
\subsubsection{Week Two}
	Everyone stood for their positions giving a small speech why they were suited to that role and then it was voted on the position that were picked were, project leader, deputy project leader, QA Manager and deputy QA manager. We also sorted out when people were available to meet up and work on the project.
\subsubsection{Week three}
	We decided to vote in a head architect as well as having an architect for web, databases and android development. This was decided because it allowed the most efficient use of the team so more people have control of management. We then started the project plan everyone was tasked jobs for the document as it had one week to be completed. The group were split into the different teams of technology depending on where people’s strengths were. A day before the deadline we met up and did a review fixing any problems that arose there and them.
\subsubsection{Week four}
	We went through the project plan with our project manager, and set tasks to fix the problems found such as requirements not matching up and traceability. 
\subsubsection{Week five}
	Design spec was set to the team and the QA team got set the testing document.
\subsubsection{Week six}
	Week six was used to tidy up the documents that had been made with reviews so they were all fit for hand in.
\subsubsection{Week seven}
	Not much was tasked due to deadline.
\subsubsection{Week eight}
	Analysing feedback for project plan and fix the changes.
\subsection{Christmas period}
	Eeveryone was set prototyping and research tasks for their specific area.
\subsection{Coding Week}
	During coding week we worked in 4 separate sections. Web, android, server side and testing. We did this split due to the lack of time to implement this project it allowed us to move resources over to different teams which needed it. I would off liked a little bit more time to fix the small things like layout in certain areas.