\subsection{Android}
    \subsubsection{Brief Description of Final Product}
        The Android app first required user details including name, phone and email. It then also requires a (pre-made on the web site) site name which is downloaded from the API on app start up. The data is then validated and on successful validation will proceed on to a specimen entry screen.

        The specimen entry screen takes a Latin plant name and a DAFOR scale represented by a slider. There is also an option for a scene and a specimen photo, which can be retaken as needed. Multiple Specimens can be added and reviewed in the specimen upload screen.

        In the specimen upload screen, specimens can be edited or deleted by long pressing on the list. They can then be uploaded to the server.

    \subsubsection{Program Structure}
        The Android app is structured into several key areas: \\
        
        \emph{Activities}\\
        Activity classes are bundled together and contain event listeners, ``AsyncTasks'' and location listeners. They also contain all the validation for input fields as well as adding lists to ``AutoCompleteTextBoxes''. \\

        \emph{Utilities}\\
        The ``Utils'' package contains SQLite database utilities and classes for adding, searching, finding and deleting data from the databases. The following databases were implemented in the app:
        \begin{enumerate}
            \item Plants - Contains the Latin names
            \item Specimens - Contains specimens the user has take for upload
            \item Users - The information the user has entered for auto-completion
            \item Sites - The sites that can be used, pulled from the API
        \end{enumerate}
        There also exists a ``OSGridReferHelper'' class which is a third party class originally to be used to convert from GPS coordinates to a os grid reference for the specimen adder. It was decided that this feature was not required and so was not used.\\

        \emph{Data Classes}\\
        These describe users, visits specimens and species and are used when reading/searching from and inserting into the database. The specimen class was not used as heavily as expected.\\

        \emph{Layout}\\
        The layout of the Android activities are described in xml files, whose names follow the ``activity\_\textless activityName\textgreater'' naming convention and are located in ``src/main/res/layouts''.

    \subsubsection{Significant Algorithms}
        The following details significant algorithms that may require alterations in the future.

        When the app starts, there is an initial ``Async Task'' thread spun off to download the sites list and update the database and to download the specimen list. This thread is located in the ``LauncherActivity'' class. This thread will check, upon download of the sites list, will add non-existent sites to the database. If the site list cannot be found, no viable error will be shown to the user, however the user may continue to use sites that already exist. The thread then proceeds to check if the latin names database is present and populated. If it contains entries, it will not download the Latin names list (as it is very large and slow to process, and so should be avoided). If it is not present, it will be downloaded and processed in a batch insertion to the database.

        There is a location listener in the ``SpecimenAdder'' activity which gets the users location via gps when adding specimens. It does not however use course (network based) location to get this. This listener implements the standard Android interface ``LocationListener''. 

        The databases are manipulated by Database Classes in the utilities package. These classes use the ``DatabaseUtilities'' class which inherit the standard ``SQLiteOpenHelper'' class. Tables are accessed via a class by their name eg ``SiteDataSource'' to access the sites table. These classes require a reference to the data class.

        Upload of the final list of reserves is done in another ``Async Task'' in the ``ReviewActivity'' where a connection to the API is established and the data from the databases serialised to JSON and uploaded. At present the JSON is constructed manually. The list of specimens is then cleared (however the UI is not updated).
    
    \subsubsection{The Main Data Areas}
        The app makes extensive use of an SQLite database to store reserves, specimens, users and species. These are manipulated by classes for each table under the ``Utils'' package, which contain methods for selecting, inserting and deleting data from the databases, via the use of data classes related to the table's content.

        The ``DataClasses'' package contains classes primarily used for storing data to be entered into or read from the database. These classes contain getters and setters for the data. They also contain an ``id'' property which is only set when the data is read from the database, this is to allow for deletion of data via it's unique id in the database.

        Finally, we use ``Adapters'' in the android API to allow ``AdapterViews'' in the activity to access data.
        adapters

    \subsubsection{Files Accessed}
        The App accesses images located on the device which were taken in the specimen selection screen. These images are located on the root of the internal storage device.

        The App also downloads the Latin names file from the remote location ``http://nic-dart.co.uk/\texttildelow~nic/res/plantlist.json'', these are then processed into the SQLite database. This is done only in the init thread.

    \subsubsection{Interfaces}
        The app required a gps device to acquire location during the specimen addition process, as well as a camera if an image is desired.

    \subsubsection{Suggestions for Improvements}
        \begin{itemize}
            \item Specimen and Scene images could be silhouetted and represent a scene and an specimen. ie. not the same image.
            \item Deleting of multiple specimens
            \item Upload completion dialogue/confirmation
            \item Users and sites are specific to specimen, not read at upload time
            \item Auto complete lists not overlapped by keyboard
            \item Settings/Preferences menu or activity
            \item Custom GPS coordinates for specimen
        \end{itemize}

    \subsubsection{Future Improvement Concerns}
        Future Activities that are made should inherit the class ``BaseActivity'', this contains methods (albeit not currently used) that will allow for consistent menu items and menu icons. 

        If significant future improvements are desired, it may be desirable to structure the app more coherently, foremost a settings or preference menu. 

    \subsubsection{Limitations of the Program}
        \begin{itemize}
            \item Deleting images before upload will most likely cause crash
            \item The ``current user'' details at the time of upload will be used.
        \end{itemize}

    \subsubsection{Building from source}
        The source contains an ``Android Studio'' project file, this contains all the links to the files needed. It will require JDK (or OpenJDK 8) and the Android API and may need to be told where they reside. Building requires either a physical Android device of version 4.0.3 (API 15) or above, or alternatively a virtual Android device, created in the AVD.

\subsection{Web}

    \subsubsection{Program Description of Final Product}

        The website is used for viewing a list of site names and being able to view a list of plants that have been found within that site. It communicates with the server using an API. A user will be able to view individual specimens as well as being able to delete and edit them.

        Upon a visit to the website the user will be taken to the Home page of the website. This page contains a brief description of how the website is to be used. The first page also contains a simple search bar which can be used to search for specimens by their name. There will also be an option to enter a password in which an admin user can log into the site to get special privileges for the website.

        The user can then go to the reserves page where a  user will be able to see a list of site names with a OS grid reference and a description. The user will then be able to have the option to view all the specimens under that reserve. When logged in then the user will see option to delete and edit the reserve as well. There will also be an option to add a reserve on this page however you can only use the add reserve functionality if you are logged into the website. The add reserve page requires the user to enter a Location name, OS grid reference and Description using a from to allow the user to enter the information.
    
        The user also has the option of viewing the all the species rather then just the reserves. On this page the species are ordered by Specimen Name by default. There are also options for searching and ordering on this page. For the ordering the it can be done through Species Name, Location Name, User, Date and Abundance by ascending or descending order. This page also uses pagination displaying and maximum of 20 specimens per page.
        
        If the user wanted to view details about a species then they would would be able to see details about; the name of the user who entered it into the database, the location where it was found,  it's unique specimenID, it's name, where it was found using an OS grid reference, it's abundance, the date it was submitted, the time and any comments about the species. They will also be able to view two photos one of the species and one of the scene. Users will be able edit and delete specimens as well. It is also possible to view the location of the plant on a Google map pop up.    

    \subsubsection{Program Structure}

        To see a detailed component diagram for the website look at SE-02-DS-00: Design Specification section 3.2, fig 2 Web Component Diagram. This shows the function scripts, web interface and the web pages used in the website.

        Within the function scripts are; logout, authentication, the  POST requests, the config. Which communicate to the Web API through JSON For a detailed list of these function scripts and how they work look at SE-02-DS-00: Design Specification, section 3.2.18, 3.2.11 and 3.2.10
    
        Within the Web interface are sub-pages of Header, Footer and Filter. For a detailed list of these sub-pages and how they work look at SE-02-DS-00: Design Specification, section 3.2.16, 3.2.14 and 3.2.24
    
        The Web Pages are Index and About these two are not dependent on the API ones pages a that are API dependent are; Reserves, Edit Reserve, Add Reserve, Plant Database, Add Specimen, Specimen and Edit Specimen. For a detailed list of these pages and how they work look at SE-02-DS-00: Design Specification, section 3.2.1, 3.2.2, 3.2.3, 3.2.4, 3.2.5, 3.2.6, 3.2.7, 3.2.8 and 3.2.9

    \subsubsection{Significant Algorithms}
        Once a JSON object has been created it is sent to the server using a curl method. The web avoids using any ``SQL'' queries by using the API. 

        The web server also uses AJAX to dynamically search and update specimen details. It also uses pagination to display a maximum number of 20 specimens and allow paging through them.
    
    \subsubsection{The Main Data Areas}
        The website stores data locally and also within sessions. In add\_specimen.php and edit\_specimen.php two arrays to create a new record; the first array is to create a new specimen and the second is to create a new record (including reserve and user details and the specimen array), this second array is then used to create the JSON object which is sent to the server via a curl method. add\_reserve.php and edit\_reserve.php also need to have the data encoded in to a JSON object in order to be sent to the server. These pages also contain an array which collects the data from a html form, the arrays then encoded into a JSON object and is sent to the server. 

    \subsubsection{Significant Files}
        The website uses html and php to gather and present data to and from the server, the site does not access any external files or directories except for `/includes/config.php' which connects the user to the server to allow for editing and deletion.

    \subsubsection{Interfaces}
        The site has been written to php version 5.5.20 and HTML5 standards and as such is able to be run on most browsers without issue. Data in the form of JSON objects are sent in the form of POST requests to the server. For further detail of the post requests to the server please check the web interface which can be found in document SE\_02\_DS\_00 section 3.1.

    \subsubsection{Suggestions For Improvements}
        When entering the password in the header to login it can be viewed. To fix this the input type of the for needs to be changed from `text' to `password'. Tidying up the code to make it easier to read and change. CSS improvements over the whole site for example, having the scene and specimen pictures the same size, button layout for buttons such as add reserve and improving the looking of the website on smaller screens. It may also be desirable to make the site responsive to suit mobile devices and small screens.
    
    \subsubsection{Future Improvement Problems}
        When adding a new page to the site that needs to be part of the session it is important to remember to put the session save path at the top of every page. As the header and footer are included on every page, changes to them will effect the entire website.

    \subsubsection{Limitations of the program}
        As the site has been written to php version 5.5.20 and HTML5 standards it may have difficulty being used in some older browsers; however, the HTML and css have been kept simple as to avoid causing issues for users of these older browsers. The site is capable of expanding if extra functionality is needed at a later date.

    \subsubsection{Building and Testing}
        In the occurrence that the website will be rebuilt and improved, the developers who are undertaking this will need to know specific information. There are two main places that the website files are located, the first being on daw54's public html directory on the Aberystwyth University server and a copy of this website on the projects GitHub repo. 
    
        The website does not require total rebuilding, as it meets the functional requirements, however, in the event that drastic improvements are made, then analysis of the current website structure and how the website communication with the Web API must be undertaken, as this is how the website functions and will continue to do so. The developer that will be improving/rebuilding must keep to these standards.
    
        If the website were to be rebuilt, the new website build would need to ensure that it is tested. The test specification is available and should be used to make sure that the website meets the functional requirements and the needs of the client. The testers will be able to see if the test passes as there is a pass criteria that if met, then the test is passed. In the occurrence there are changes to the programming which has created a problem with the functionality, then additional tests must be added to the website test specification. This is very easily done, as the test specification was created using Latex. The user can simply see how previous test rows were created where they will be able to then understand how to implement a new test into the Latex document. 

\subsection{Server}
    \subsubsection{Brief Description of Final Product}
        The server is a combination of a Database and an application programming interface. It acts as the bridge between the Android device and the website to the Database, further protecting the database from direct access. This allows code, sensitive information and data to be stored in a non-accessible place. The server contains a relational database which holds all the data important for the system: specimens, reserves, records and users. To access this data, the website and the android application must use the API PHP script commands which run validation, sanitisation and SQL queries using JSON data structures. 

    \subsubsection{Program Structure}
        The server API is a list of commands that are to be run by the android application and the website to access and manipulate data in the Database. The Design Specification document contains all the information about the program structure.

        For a list of the commands in use in the system and what they do, please see the document SE\_O2\-DS\_00: Design Specification, section 1.5: Significant Server Components. For a detailed list of how the commands work including their required POST requests, their return status codes and required headers, please see the document SE\_O2\_DS\_00: Design Specification, section 4.1.3: Server Interface. For an example sequence diagram of the most complex command (addRecord.php), please see document SE-02-DS-00: Design Specification, section 4.1.13. All other commands follow a simplified sequence to this. For the Component Diagram of the server, please see document SE\_02\_DS\_00: Design Specification, section 4.2.1: Detailed Design: Diagrams. 

    \newpage
    \subsubsection{Significant Algorithms}
        Validation and Sanitisation:

        To validate data inputs we ensure strings are not empty and we ensure latitude and longitudes are valid as true values. Ensuring strings are not empty: 
        
        \begin{lstlisting}[language=php]
if(empty($locationName) || empty($locationOS))
{
    die();
    return status code 400;
}
        \end{lstlisting}

        Ensuring latitude and longitude values are true:
    
        \begin{lstlisting}[language=php]
if($Latitude > 90 || $Latitude < -90 || $Longitude > 180 || $Longitude < -180)
{
    die();
    return status code 400;
}
        \end{lstlisting}

        To sanitise all the data inputs, the command real\_escape\_string() was used on all POST data received from the website: 
        
        \begin{lstlisting}[language=php]
$SpeciesName = $conn->real_escape_string($specimen->SpeciesName);
        \end{lstlisting}
        
        This prevents any malicious data from touching the database.

        SQL Queries were used to retrieve/manipulate data in the database:

        Add:
        \begin{lstlisting}[language=sql]
"INSERT INTO botany_users (user_name, user_phone, user_email) VALUES ('$UserName', '$UserPhone', '$UserEmail')"
        \end{lstlisting}

        Update:
        \begin{lstlisting}[language=sql]
"UPDATE botany_reserves SET location_name='$LocationName', location_os='$LocationOS', description='$Description' WHERE reserve_id = $ReserveID"
        \end{lstlisting}
            
        Get:
        \begin{lstlisting}[language=sql]
"SELECT * FROM botany_reserves WHERE reserve_id=$reserveID"
        \end{lstlisting}
        
        Remove:
        \begin{lstlisting}[language=sql]
"DELETE FROM botany_reserves WHERE reserve_id = $reserveID"
        \end{lstlisting}

        We manually manipulate the committing for the SQL queries to ensure no invalid data gets added. All checking is done, and then we tell it to commit. This allows to reverse any affected data if it proves to be wrong.

        We provided the ability to authenticate a password input to ensure the user was authorised to use commands:
        \begin{lstlisting}[language=php]
if(!strcmp($password, $CONFIG['adminPassword']))    
{
    echo "true";
}
else
{
    echo "false";
}
        \end{lstlisting}
    
    We wrote SQL queries to create the database tables, e.g:
    \begin{lstlisting}[language=sql]
        create table botany_records ( 
        record_id INT AUTO_INCREMENT , 
        user_id INT NOT NULL, 
        time_stamp INT,
        reserve_id INT,
        PRIMARY KEY (record_id));
        
        alter table botany_records
        add foreign key (user_id)  
        references botany_users(user_id)  
        on delete cascade on update cascade;
    \end{lstlisting}

    \subsubsection{The Main Data Areas}
        To transfer data from the android application and the website to the database,  the data had to be structured in a JSON file format. JSON was a nice, flexible and easy to use language, allowing us to quickly and easily create data structures to be decoded by the API. To do this, the commands json\_encode() and json\_decode() are used. For example, if a new specimen was being added by the website, the website will json\_encode(specimen array), and the server will json\_decode the POST data. If a specimen is being sent to the website, the server will json\_encode(specimen array) and the website will json\_decode(POST data). To see each specific JSON data structure, please see document SE-02-DS-00: Design Specification, section 4.2.2: Significant Data Structures. This section also details the config file for use when changing resource locations and passwords. 

    \subsubsection{Files Accessed}
        The API accesses the resources directory defined in `/includes/config.php' heavily. One should refrain from manually accessing the contents of that directory, and altering the directory structure. The PHP scripts should be allowed read/write access to said directory. The API does not access files outside of the resources directory.

    \subsubsection{Interfaces}
        The server's PHP scripts that implement the web API functionality use the JSON standard to receive structured data from and transmit structured data to its clients. JSON is used in conjunction with the widely accepted HTTP protocol, the JSON being carried in either the POST headers (in client requests), or the HTTP response body (in server responses).
    
        All web API commands need to be called via the HTTP protocol using the POST method, and need to be supplied the required parameters (either plain text, or JSON format, described in detail in the design specification).
        
        A common settings interface is used for storing environmental variables such as database credentials, administrator password, and server root. Those are all stored in /includes/config.php inside the API directory.

    \subsubsection{Suggestions for Improvements}

        A number of improvements could be made, although the basic functionality of the API is complete up to the specification standard.
    
        The choice of platform and programming language for the API was limited to the available technologies on Central. This does not represent a real-life situation, where the developers would likely have administrative control over the server the API is hosted on, allowing them a more flexible choice of technology and platform. Discarding PHP in favour of a more modern
        language: 
        \begin{itemize}
            \item Would reduce future maintenance issues.
            \item Would have sped up the development of the product, and will speed up the development of any future improvements.
            \item Make quality assurance easier and more efficient.
            \item Could potentially reduce the hardware requirements of the API, depending on the selected replacement technology stack (Java EE/ASP.NET).
        \end{itemize}

        Therefore, a transition from PHP to Ruby on Rails, Python+Django, or even Node.js would bring long-term benefits to the project, with Java EE and ASP.NET bringing immediate savings from hardware and electricity costs.
    
        Another, more specific improvement, is the inclusion of `pretty URLs'. An example of that would be the current `/getResouce.php' web method, which could be rewritten as `/resource/{id}' followed by the desired resource ID. This requires relaxation of the requirement to use POST requests exclusively, as in many cases GET requests make more sense (a RESTful approach would suit the use-case perfectly, in fact). Another example: `/reserve/remove/{id}' replacing `/removeReserve.php'.

    \subsubsection{Future Improvement Concerns}

        Separate web methods in the web API are reasonably separated. A change in one method should not induce undesired changes in others. However, all methods share a single point of communication, the database, and therefore a single point of failure . The database structure is rigidly defined, and as of now, the code base does not allow one to easily change table and column names. This means that any changes to the database schema, even trivial ones such as renames, need to be carefully accounted for in the API source code, and thoroughly tested before being released into production.
    
        While separate web methods are independent of each other, the same can not be said of the separate routines that constitute the methods. The code was produced in a rush, and little to no time was left for refactoring. Many parts of the source code are therefore in the form of long, function-less scripts, with no modularity whatsoever. Therefore, extra caution should be practised when editing: a change in one variable, or a slight rearrangement of the statement order could generate unexpected behaviour in seemingly unrelated sections of code in the same file.

    \subsubsection{Limitations of the Program}
        As an interpreted language, PHP is fairly slow compared to compiled and JIT-compiled languages. For low-to-moderate size use cases, it's performance is perfectly reasonable, but it lacks the high scalability offered by some competing technologies. 
    
        The technical limitations are, therefore, modest: a mainstream 2006-era CPU such as a Core 2 Duo, and 1GB of RAM, would have little issue running the API provided it is not heavily used. As the incoming requests rise, though, hardware will begin to fail to meet the demand, requiring higher-performance hardware. Eventually, one would not be able to obtain a faster computer, and load balancing across several machines becomes necessary, which the API architecture does not allow at the moment (as it uses local file storage to save resources). At this point, resource storage would need to be moved to a separate server, and the API source code would require change. 
    
        Regarding the database: MySQL is a good database engine for all but the highest-performance scenarios. Switching the database engine to InnoDB will bring further performance benefits, but that would remove the support for referential integrity, currently built into the DB schema, and support for transactions, used by the API. Workarounds can be implemented, however. Considering the project lacks the ability to provide a revenue stream of any sort, purchasing expensive licences for more capable databases such as Oracle Database or Microsoft SQL Server is inconceivable, and according to projections, unlikely to ever become necessary.

    \subsubsection{Building from source}
        The web API requires no rebuilding. Copying the API files inside the Apache `public\_html' directory, with PHP installed of course, should suffice.
    
        The database can be set up by executing the table creation scripts (found at 'table\_queries.txt) on a blank MySQL database.
    
        Once the database is set up, one should edit the `/includes/config.php' file and configure it with the database address, name, username and password, the path to the server root, and the path to the resources storage. An admin password should also be picked at this point. Ensure all PHP scripts have write access to the resources directory.