\subsection{Android User}
Individual Module Testing will be left to the coder, and tests should be written before the coding is done.

Test Ref Req Being Tested Test Content Input Output Pass Criteria

SE-F-001 FR1 Startup of Software Start up Android app Android App should open. Android app opens without error.

SE-F-002 FR2 Valid username/password allows user to login Enter valid username/password App should confirm successful login and proceed to App. App confirms successful login and proceeds to the App.

SE-F-003 FR2 Invalid username/password does not allow user Enter invalid username/password combination. App should state that it was an App states that the login details

to login invalid login and does not allow user to login. are invalid, stays on login page.

SE-F-004 FR3 User allowed to add a plant name to the database. Enter plant name to the database via android app. States that plant details are successfully added to the database. Plant details successfully added to the database.

SE-F-005 FR4 User allowed to add Species Details. Enter Species Details to the database via android app. States that plant details are successfully added to the database. Plant details successfully added to the database.

SE-F-006 FR4 User not allowed to enter invalid Species Details to the database. Enter invalid Species Details to the database via android app. App states that the details entered are invalid. Does not enter to database. Returns to input page.

SE-F-007 FR4 User allowed to add a picture of a plant to the database. Enter a plant picture to the database via android app. States that plant picture is successfully added to the database. Plant picture successfully added to the database.

SE-F-008 FR4 User not allowed to add a non-image file when prompted for a picture of a plant. Attempt to enter a non-image file to the database. States that the file is not an image file. Does not enter to database. Returns to input page.

SE-F-009 FR4 User not allowed to add a picture of a plant to the database if over a certain size (to be discussed with group.) Attempt to enter an absurdly large image file to the database (e.g 20MB). States that the file exceeds filesize limits. Does not enter to database. Returns to input page.

SE-F-010 FR4 User allowed to record the level of abundance of the plant within the area. Record level of abundance of plant within the area. Enter a valid input. States that abundance of plant is successfully added to the database. Level of abundance successfully added to the database.

SE-F-011 FR4 User not allowed to Attempt to enter an States that Does not

enter an invalid input for abundance of plant. invalid input for abundance of plant. the input is invalid. enter to database, returns to input page.

SE-F-012 FR6 Application should know whether it is connected to the internet, and that it is able to send records to the database. If not, the data is stored in local storage. Attempt to use app whilst connected to the internet. States that records successfully sent to the database. Successfully sends records to the database.

SE-F-013 FR6 Application should know whether it is connected to the internet, and that it is able to send records to the database. If not, the data is stored in local storage. Attempt to use app whilst not connected to the internet. States that the app is not connected to the internet and that the records were stored in local storage. Stores the records on local storage.
\subsection{Website User}
Individual Module Testing will be left to the coder, and tests should be written before the coding is done.

Test Ref Req Being Tested Test Content Input Output Pass Criteria

SE-F-014 FR2 Valid Username/Password allows user to login. Login with valid Username/Password.

SE-F-015 FR2 Invalid Username/Password does not allow user to login. Login with invalid Username/Password.

SE-F-016 FR3 User allowed to add a plant name to the database. Enter valid plant name using the website. States that plant details are successfully added to the database. Plant details successfully added to the database.

SE-F-017 FR3 User not allowed to add an invalid plant name to the database. Enter invalid plant name using the website. States that the plant name is invalid. Plant details not added to database, returns to

input page.

SE-F-018 FR4 User allowed to add Species Details. Enter valid Species Details using the website. States that plant details are successfully added to the database. Plant details successfully added to database.

SE-F-019 FR4 User not allowed to add invalid Species Details. Enter invalid Species Details using the website. States that plant details are invalid. Plant details not added to database, returns to input page.

SE-F-020 FR4 User allowed to add a picture of a plant to the database. Enter a valid image file to the database using the website. States that plant image is successfully added to the database. Plant image successfully added to the database.

SE-F-021 FR4 User not allowed to add a non-image file when prompted for picture of a plant. Attempt to enter a non-image file. States that the file is not a valid image file. Image not added to database, returns to input page.

SE-F-022 FR4 User allowed to record the level of abundance of the plant within the area. Enter level of abundance of the plant using the website. States that plant abundance is successfully added to the database. Plant abundance successfully added to the database.

SE-F-023 FR5 User able to make changes to any record that they have added to the database. Attempt to change Plant Name of a user inputted plant. States that change was successfully made. Change successfully made to the database.

SE-F-024 FR5 User able to make changes to any record that they have added to the database. Attempt to change Species Details of a user inputted plant. States that change was successfully made. Change successfully made to the database.

SE-F-025 FR5 User able to make changes to any record that they have added to the database. Attempt to change plant picture of a user inputted plant. States that change was successfully made. Change successfully made to the database.

SE-F-026 FR5 User able to make changes to any Attempt to change abundance details of States that change was Change successfully

record that they have added to the database. a user inputted plant. successfully made. made to the database.

SE-F-027 FR5 User able to remove any record that they have added to the database. Attempt to remove a user-added record from the database. States that record was successfully removed. Record successfully removed from the database.

\subsection{Admin}

Individual Module Testing will be left to the coder, and tests should be written before the coding is done.

Test Ref Req Being Tested Test Content Input Output Pass Criteria

SE-F-028 FR7 Server allows a user to login to the application through the android app providing they use a valid username/password. See SE-F-002 See SE-F-002 See SE-F-002

SE-F-029 FR7 Server allows a user to login to the application through the website providing they use a valid username/password. See SE-F-014 See SE-F-014 See SE-F-014

SE-F-030 FR7 Server does not allow a user who attempts to login using the android app without a valid username/password. See SE-F-003 See SE-F-003 See SE-F-003

SE-F-031 FR7 Server does not allow a user who attempts to login using the website without a valid username/password. See SE-F-015 See SE-F-015 See SE-F-015

SE-F-032 FR9 When user wants to view, edit, or delete records they have entered, the server calls them from the database. See SE-F-026, See SE-F-027 See SE-F-026, See SE-F-027 See SE-F-026, See SE-F-027

SE-F-034 FR9 Server must be able to send and receive data from the phone of records being entered See SE-F-004 See SE-F-005 See SE-F-007 See SE-F-010 See SE-F-004 See SE-F-005 See SE-F-007 See SE-F-010 See SE-F-004 See SE-F-005 See SE-F-007 See SE-F-010

SE-F-036 FR5 The website admin should be able to remove any record entered into the Admin attempts to remove a record Confirm that record has been changed. Record changed in database.

database by any user entered by a user.

SE-F-037 FR8 The database administrator will be able to log into the database and manage/maintain it, if they provide correct login details. Attempt to login with valid details. Confirm login. Admin now able to manage/maintain database.

SE-F-038 FR8 The database will not allow someone to login without providing valid login details. Attempt to login with invalid details. State that login details are invalid. Admin not logged in.
